### 2021-04-12 LaTeX-USENIX/sections/paper.tex
revisions

%A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}). In the case of (1), validating the proof must be cheaper than running the function itself. There are two main approaches to (1): the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}), and the second is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.}
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

There are two broad roll-up categories (i) \textit{zero knowledge} and (ii) \textit{optimistic} roll-ups, each taking a different approach to ensure the validity of off-chain transaction executions. A zero knowledge roll-up (\textit{a.k.a.} ZK-rollup) uses cryptographic validity proofs (SNARKS~\cite{BCGTV13,GGPR13}) which can be later verified on-chain. These proofs are heavy to compute (introduce a burden to the validators who generate them) but considered valid once posted to the Ethereum. An optimistic roll-up uses a side chain (a roll-up chain) that is run on top of Layer 1. Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions. Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost. Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.

Arbitrum is an Ethereum scaling Layer 2 solution that operates an optimistic roll-up~\cite{kalodner2018arbitrum}. The roll-up chain is run on top of the Ethereum blockchain and contains all the Arbitrum contracts (called ArbOS). There is a  bridge contract (called the EThBridge) that resides on the Ethereum and serves as a bridge between two chains. To execute a transaction on a DApp that is running on Arbitrum, a user first sends a transaction to the bridge contract. This transaction only contains the instructions for calling a function and the data required for it. As as soon as this transaction is included in the Ethereum block, it will get timestamped and ordered. A validator, who is constantly watching the bridge contract for new transactions, sees the transaction, executes it and asserts the result of the execution to the ArbOS. Once the dispute challenge period is over, the transaction is final and the new state of the ArbOS will be inserted into the Ethereum. The bridge contract maintains all the data required for verification using which anyone can compute the state of the ArbOS and assure the executions have been performed correctly.

\textit{Testing Platforms.} Arbitrum currently operates a test newtork with a bridge contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge contract}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum. These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).

\input{tables/performance_Arbitrum.tex}

\textit{Performance Evaluations.} Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum. The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH. Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}. Th last column of the Table shows the actual cost of executing the transaction that is measured in ArbGas paid by the validators. ArbGas is basically used to measure the validators' resource usage and is significantly cheaper than Layer 1 gas (currently the testnet has 100 ArbGas for every Layer 1 gas unit, this ratio is even likely to improve in Arbitrum's next versions).

 Table~\ref{tab:arbitrum_performance} shows that Arbitrum reduces the cost for executing the trades by around 99.9\% (a \cm variant implemented with linked list can handle 152 pairs of trades at most with the cost of 5,495,265 gas, while on Arbitrum the cost is 1,325 gas). Note that when using \cm on Arbitrum, we can basically process an infinite number of orders. In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs cost 1,544 gas and ass the pairs increase, the cost is essentially constant. Submitting an order costs 2,005 gas on average as opposed to 207,932 on-chain.

@@

>>>>

@@

A function can be computed off-chain and the new state of the DApp, called a \textit{rollup}, is written back to the blockchain, accompanied by either (1) a proof that the function was executed correctly, or (2) a dispute resolution process that can resolve, on-chain, functions that are not executed correctly (\eg Arbitrum~\cite{kalodner2018arbitrum}). In the case of (1), validating the proof must be cheaper than running the function itself. There are two main approaches: (1a) the first is to use cryptographic proof techniques (\eg SNARKS~\cite{BCGTV13,GGPR13} and variants~\cite{BBHR19}). This is called a \textit{zk-rollup}. Note that the proofs are heavy to compute (introducing a burden to the validators who generate them) but considered valid once posted to the Ethereum. The second approach (1b) is to execute the function in a trusted execution environment (TEE; \eg Intel SGX) and validate the TEE's quote on-chain (\eg Ekiden~\cite{cheng2019ekiden}).\footnote{The TEE-based approach is mired by recent attacks on SGX~\cite{SGX1,SGX2,SGX3,SGX4}, however these attacks do not necessarily apply to the specifics of how SGX is used here, and safer TEE technologies like Intel TXT (\cf~\cite{ZBC+19}) can be substituted.} Approach (2) is called an \textit{optimistic roll-up}. Although the dispute time delays result in a slower transaction finality, optimistic roll-ups substantially increase the performance by decreasing the gas cost.

%It uses a side chain (a roll-up chain) that is run on top of Layer 1. Once the executions are performed, validators assert the new states of the roll-up chain to the Ethereum and wait for anyone to dispute these assertions.

%Therefore, we choose this roll-up solution to for the Layer 2 implementation of \cm.

Arbitrum is an Ethereum Layer 2 scaling solution that operates as an optimistic roll-up~\cite{kalodner2018arbitrum}. Arbitrum runs entire DApps inside its environment, which acts like a container and requires special bridge contacts to interact with `normal' (or L1) Ethereum DApps. To deploy a DApp on Arbitrum, or to execute a function on an existing Arbitrum DApp, the transaction is sent to an L1 Arbitrum contract called an inbox. The transaction is not executed, it is only recorded (as calldata) by the inbox contract. Like any other transactions on Ethereum, miners determine the order of the transactions sent to the inbox. A set of validators (open to anyone) are watching the inbox contract for new transactions. Once an inbox transaction is finalized in an Ethereum block, validators will execute the transaction and asserts the result of the execution to other validators on a sidechain called ArbOS. Once the dispute challenge period is over, the new state of ArbOS will be inserted into Ethereum. As the inbox contract maintains all Arbitrum transactions, anyone can recompute the entire current state of the ArbOS and file a dispute if executions are not performed correctly. Disputes are adjudicated by Ethereum itself and require essentially constant gas costs, regardless of the size of the gas costs of the transaction being disputed.

\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract called the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum. These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).

%\input{tables/performance_Arbitrum.tex}

%Table~\ref{tab:arbitrum_performance} compares the cost of executing the maximum number of trades on Ethereum (Kovan testnet) and executing the same number of trades when running \cm on Layer 2 with Arbitrum. The fourth column of the Table represents the Ethereum gas cost for relaying the transaction to the Arbitrum EthBridge contract and is paid in ETH. Note that here we report the cost of sending the transaction directly to the Arbitrum EthBridge contract and not through the aggregator~\footnote{The Layer 1 cost reported on the Kovan block explorer represents the gas cost related to the entire batch of transactions.}.

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that without a rollup, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the callmarket() function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

While the runtime of a transaction is no longer an issue for Ethereum, it is still an issue for the validators. Like Ethereum miners, validators do measure the amount of gas (called ArbGas in Arbitrum) a transaction takes although Arbitrum emmulates EVM code with its own different OpCodes. Thus, ArbGas with a roll-up and L1 gas without a roll-up are not directly comparable but both increase and decrease proportionately with the complexity of running the function. Closing a market with 38 pairs costs 46,705,693 ArbGas. Until Arbitrum deploys on mainnet, the price of ArbGas in Gwei (or USD) is unknown but it is thought to be relatively very cheap.
